Visualizing demographic evolution using geographically inconsistent census data

### 2019-10-13 paper/method.tex
not working

Each trajectory represents a different temporal path through the clusters.
Therefore the trajectories encode how the demographic characteristics changed
over time. These changes are summarised by the two sections identified as
\emph{how} in Figure~\ref{fig:ui}. In the left panel, there is a Sankey diagram
where each ribbon represents a different trajectory. Since the associated
regions have different population numbers, the width of each ribbon is
proportional to the smaller of the populations involved, pairwise. This
approximation works well in general, but leads to small inconsistencies in some
specific cases. For instance, in the results for Miami, which is available in
the supplementary material, the combined width of the ribbons decreases
slightly, despite an increase in the population numbers.

>>>>

Each trajectory represents a different temporal path through the clusters.
Therefore the trajectories encode how the demographic characteristics changed
over time. These changes are summarised by the two sections identified as
\emph{how} in Figure~\ref{fig:ui}. In the left panel, there is a Sankey diagram
where each ribbon represents a different trajectory. Since the associated
regions have different population numbers, the width of each ribbon is
proportional to the smaller of the populations involved, pairwise. This
approximation is necessary to interpolate two different population numbers into
one and it works well in general, but it can lead to inconsistencies in some
specific cases, where some regions can be counted more than once. For instance,
in the results for Miami, which is available in the supplementary material, the
combined width of the ribbons decreases over time, despite an increase in the
population numbers. However, the population numbers presented in the bottom part
of the interface are correct.
